Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-21 paper/main.tex
suppl.: additional contrasts

\subsection{Additional contrasts: PPA, RSC, and LOC (AV \& AV)}

\todo[inline]{SE: use different colormap for overlap of contrasts' clusters}
\todo[inline]{SE: wie unterscheiden sich die Kontraste?}
\todo[inline]{Wo sind welche Kontraste (z.B. im Ergebnis) von anderen abgewichen?}

% intro
In order to test the robustness of our approach, we created overall five
$t$-contrasts for the movie stimulus (Tab.~\ref{tab:av-contrasts}), and overall
eight $t$-contrast for the audio-description stimulus
(Tab.~\ref{tab:av-contrasts}).
% how
Contrasts differ in contrasted categeories based on ``how well'' averaged
events within categories were considered to represent spatial and non-spatial
information, and the number of events in the stimulus.
% NeuroVault
Unthresholded $Z$-maps of all contrasts on a group level as well as individual
results of the primary $t$-contrasts co-registered to the group-template (MNI152
space) can found at NeuroVault
\href{https://neurovault.org/collections/KADGMGVZ/}{\url{neurovault.org/collections/KADGMGVZNeuroVault}}.

@@

% AV results: PPA; biggest overlap in posterior part of PPA group overlap  =
% temporal occipital fusiform cortex
All five movie contrasts yielded significant bilateral clusters that
overlap with the PPA group overlap (Fig.~\ref{fig:stability-slices}).
% AV: RSC & LOC
Also reliably across contrasts of the movie stimulus, we find bilaterally
significant clusters in the ventral precuneal cortex and posterior
cingulate gyrus (i.e. restrosplenial complex; contrasts 1, 4, 5), and lateral
occipital cortex (contrasts 1, 2, 4, 5).

@@

% AD: results
For the audio-description stimulus, all contrasts except contrast 7
(\texttt{se\_new}, \texttt{se\_old} > non-spatial categories) and contrast 8
(\texttt{se\_new} > non-spatial categories) yielded significant bilateral
clusters in anterior regions of the group PPA overlap
(Fig.~\ref{fig:stability-slices}).
% AD: RSC & LOC
We find bilaterally significant clusters also in the ventral precuneus (all
except contrasts 8), lateral occipital cortex (bilateral in contrasts 1 to 4;
unilateral in contrasts 6 and 7).
% "Discussion" of PPA, RSC, and LOC
The results across the contrasts of the movie and audio-description stimulus
indicate that our findings regarding the PPA but also RSC and LOC are robust and
do not depend on the design of one specific contrasts.
% but
Nevertheless, results are sensitive to the contrasted categories and the amount
of available data.
% example
For example, contrast 8 of the audio-description stimulus (\texttt{se\_new} > \texttt{se\_old})
that used the most heterogeneous categories comprising the least amount of
events yielded neither a significant cluster in the right-hemispheric nor
left-hemispheric PPA.
% concluding statement
Hence, investigators that use model-driven analyses have to consider how many
events a naturalistic stimulus may provide and how homogeneous the events to be
averaged might be.

@@

\begin{comment}
    the mother of total confusion: Aminoff shifts the PPA along the
    anterior-poster axis depending on publication;
    in Aminoff (2007, 2013):
    anterior PPA = spatial associations,
    region anterior to (!) PPA = non-spatial associations;
    in Aminoff (2015):
    posterior PPA = spatial associations,
    anterior PPA = non-spatial associations;
    hence: complete bullshit;
    ignore Aminoff (2015) due to various reasons
\end{comment}

\subsection{Additional contrasts: let's talk about left overs}

\todo[inline]{look at the events within categories \& give some counts}

\todo[inline]{compare with Michaels make over of text regarding confound
structure

\todo[inline]{main message here again: you need events! (and be aware of biases)}

%
Three contrasts yielded bilaterally significant clusters in superior temporal
cortices (contrasts 3, 6, 7), one contrast a unilateral right cluster (contrast
2).
%
\todo{following is (probably too) exhaustive}
%
Lastly, some contrasts of the audio-description stimulus yielded significant
clusters in regions that were not statistically significant in three or more
contrasts.
%
Contrast 2 yielded clusters in the anterior cingulate gyrus (bilateral), right
frontal pole, right frontal medial cortex, and right putamen.
%
Contrast 3 shows clusters in the anterior cingulate gyrus (bilateral), left
frontal pole, and left insular.
%
Contrast 7 shows clusters in the left frontal pole and left frontal operculum,
left insular.
%
Contrast 6 shows one additional cluster in the right medial frontal cortex.
% concludion statement
Conclusion: This can be attributed to the uncontrolled nature of averaged events.

% ``confounding'' clusters
Our whole brain analysis did not identify systematically occuring clusters pointing
to confounding cognitive processes like attention or eye movements
% AV: null results regarding attention and eye movements
% AD: auditory cortices
Nevertheless, for the audio-description stimulus contrasts that compare verbal
hints of the change of a setting (\texttt{se\_new} or \texttt{se\_old}) to all
non-spatial categories (cf. contrasts 2, 3, 6, 7) show clusters in
(primary and secondary) auditory cortices.
% averaging vs. nuisance regressors
This suggests that variance correlating with lower level auditory processes was
not averaged out across events and the employed nuisance regressors did not
capture this variance appropriately.
% possible reason
Activity in such clusters could be correlated with a possible
change of the soundscape when the narrator of the audio-description,
corresponding to a cut in the movie, switches udio-description stimulusto a another setting.
% concluding statement
Thus, investigators that use model-driven methods to investigate brain functions
using naturalistic stimuli should extensively annotate the stimulus material
and test for correlations among variables.

\todo[inline]{random [?] prefrontal cluster in 2-3 AD contrasts; at the moment
no idea what the correlating process could be; be aware of reverse inferences}

>>>>

\subsection{additional contrasts}

\todo{print contrasts; count per category? -> pattern "average of events" and
counts vs. significant clusters?}

\subsubsection{PPA, RSC, and LOC (AV \& AV)}

\todo[inline]{SE: use different colormap for overlap of contrasts' clusters}
lche Kontraste (z.B. im Ergebnis) von anderen abgewichen?}

% intro
In order to test the robustness of our approach, we created overall five
$t$-contrasts for the movie stimulus (Tab.~\ref{tab:av-contrasts}), and overall
eight $t$-contrast for the audio-description stimulus
(Tab.~\ref{tab:av-contrasts}).
% how
Contrasts differ in contrasted categeories based on ``how well'' averaged events
within categories were considered to represent spatial and non-spatial
information, and the number of events in the stimulus.
% NeuroVault
Unthresholded $Z$-maps of all contrasts on a group level co-registered to the
group-template (MNI152 space) can found at NeuroVault
\href{https://neurovault.org/collections/KADGMGVZ/}{\url{neurovault.org/collections/KADGMGVZNeuroVault}}.

@@

% AV results: PPA; biggest overlap in posterior part of PPA group overlap  =
% temporal occipital fusiform cortex
Reliably across all five movie contrasts, we find bilaterally significant
clusters that overlap with the PPA group overlap
(Fig.~\ref{fig:stability-slices}).
% AV: RSC & LOC
Results of the movie also yielded significant clusters in the ventral precuneal
cortex and posterior cingulate gyrus (i.e. restrosplenial complex; contrasts 1,
4, 5), and lateral occipital cortex (contrasts 1, 2, 4, 5).

@@

% AD: results
In results from the analysis of the audio-description, all contrasts except
contrast 7 (\texttt{se\_new}, \texttt{se\_old} > non-spatial categories) and
contrast 8 (\texttt{se\_new} > non-spatial categories) yielded significant
bilateral clusters in anterior regions of the group PPA overlap
(Fig.~\ref{fig:stability-slices}).
% AD: RSC & LOC
Results from the analysis of the audio-description also yielded bilaterally
significant clusters in the ventral precuneus (all contrasts except contrasts 8)
and lateral occipital cortex (bilateral in contrasts 1 to 4; unilateral in
contrasts 6 and 7).
% concluding stament regarding PPA, RSC, and LOC
The results across the contrasts of the movie and audio-description indicate
that our findings regarding the PPA but also RSC and LOC are robust and do not
depend on the design of one specific contrasts.
%
\todo[inline]{print contrasts; counts per contrasted categories? "fit of
averaged events"?}
% but
Nevertheless, results are sensitive to the contrasted categories and the amount
of available data.
% example
For example, contrast 8 of the audio-description stimulus (\texttt{se\_new} >
\texttt{se\_old}) that used the most heterogeneous categories comprising the
least amount of events yielded neither a significant cluster in the
right-hemispheric nor left-hemispheric PPA.
% concluding statement
Hence, investigators that use model-driven analyses have to consider how many
events a naturalistic stimulus may provide and how homogeneous the events to be
averaged might be.

\subsubsection{auditory cortices}

Further, some contrasts yielded bilaterally significant clusters in superior
temporal cortices (contrasts 3, 6, 7) and one contrast a unilateral right
cluster (contrast 2).
% AD: auditory cortices
Thus, increased hemodynamic activity in the superior temporal cortex is apparent
in that compare verbal hints of the change of a setting (\texttt{se\_new} or
\texttt{se\_old}) to all non-spatial categories (cf. contrasts 2, 3, 6, 7) show
clusters in (primary and secondary) auditory cortices.
% soundscape
Activity in such clusters could be correlated with a possible change of the
soundscape when the narrator of the audio-description, corresponding to a cut in
the movie, switches udio-description stimulusto a another setting.
% interpretation 1
This suggests that variance correlating with lower level auditory processes was
not averaged out across events and the employed nuisance regressors did not
capture this variance appropriately.\todo{this sounds shitty}
% interpretation 2
Increased hemodynamic activity in superior temporal cortices suggest a bias
towards lower-level auditory perceptual processes on the positive side of the
GLM contrasts.

\subsubsection{``random clusters''}

\todo[inline]{following list probaly exhaustive but probably too long}
%
Lastly, some contrasts of the audio-description stimulus yielded significant
clusters in regions that were not statistically significant in three or more
contrasts.
% details
In detail, contrast 2 yielded clusters in the anterior cingulate gyrus
(bilateral), right frontal pole, right frontal medial cortex, and right putamen.
%
Contrast 3 shows clusters in the anterior cingulate gyrus (bilateral), left
frontal pole, and left insular.
%
Contrast 7 shows clusters in the left frontal pole and left frontal operculum,
left insular.
%
Contrast 6 shows one additional cluster in the right medial frontal cortex.
% concludion statement
Here again, significantly increased activation beyond areas known to be involved
in processing of spatial information can be attributed to stimulus features of
the naturalistic stimulus that were not sufficiently controlled leading to a
bias in the contrasts.

@@
